### 2018-01-29 Documents/bootcamp_syllabus.tex
doument update

This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems. We have a myself and a teaching fellow to help. Below is the contact info for our teaching fellow this semester.

\textbf{Teaching Fellows}\\
\\
Vineetha Kutty \\
Email: \href{mailto:vkk242@nyu.edu}{vkk242@nyu.edu}\\
Office hours: TBA\\

The bottom line:  {\bf If you're stuck, ask for help\/}.
Really.  Don't be a hero, ask for help.

@@

Ethics, disabilities, and many other things are governed by NYU
and Stern policies.
If you have questions about them, please ask.

On graded work:
You may discuss assignments with anyone (in fact, we encourage it),
but anything you submit, including your code, should be your own.
Exams should be entirely your own work.

On disabilities:
If you have a qualified disability that requires academic accommodation,
please contact the Moses Center for Students with Disabilities
(\href{http://www.nyu.edu/life/safety-health-wellness/students-with-disabilities.html}{CSD},
212-998-4980) and ask them to
send us a letter verifying your registration and outlining the accommodation they recommend.
If you need to take an exam at the CSD,
you must submit a completed Exam Accommodations Form to them
at least one week prior to the scheduled exam time to be assured accommodation.

>>>>

This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems. The bottom line:  {\bf If you're stuck, ask for help\/}.
Really.  Don't be a hero, ask for help.

We have a myself and a teaching fellow to help. Below is the contact info for our teaching fellow this semester.

\textbf{Teaching Fellows}\\
\\
Vineetha Kutty \\
Email: \href{mailto:vkk242@nyu.edu}{vkk242@nyu.edu}\\
Office hours: TBA\\
\\
\textbf{My email policy.} During day time on weekdays, I generally answer email (\href{mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}) quickly. During evenings and weekends, you should expect that my response will be less prompt. My official policy is that I reserve the right to get back to you within 24 hours. If I don't, feel free to email me again.\\

@@

\begin{itemize}
\item \textbf{General Behavior.} The School expects that students will conduct themselves with respect and professionalism toward faculty, students, and others present in class and will follow the rules laid down by the instructor for classroom behavior.  Students who fail to do so may be asked to leave the classroom.

\item \textbf{Collaboration on Graded Assignments.} You may discuss assignments with anyone (in fact, we encourage it), but anything you submit, including your code, should be your own. Exams should be entirely your own work. Violation of this policy will result in a failing grade for the course.

\item \textbf{Academic Integrity.}
\begin{itemize}
\item Integrity is critical to the learning process and to all that we do here at NYU Stern. As members of our community, all students agree to abide by the NYU Stern Student Code of Conduct, which includes a commitment to:
\item Exercise integrity in all aspects of one's academic work including, but not limited to, the preparation and completion of exams, papers and all other course requirements by not engaging in any method or means that provides an unfair advantage.
\item Clearly acknowledge the work and efforts of others when submitting written work as one's own. Ideas, data, direct quotations (which should be designated with quotation marks), paraphrasing, creative expression, or any other incorporation of the work of others should be fully referenced.
\item Refrain from behaving in ways that knowingly support, assist, or in any way attempt to enable another person to engage in any violation of the Code of Conduct. Our support also includes reporting any observed violations of this Code of Conduct or other School and University policies that are deemed to adversely affect the NYU Stern community.
\end{itemize}
The entire Stern Student \href{http://www.stern.nyu.edu/sites/default/files/assets/documents/con_039512.pdf}{Code of Conduct} applies to all students enrolled in Stern courses. Discussion of this code of conduct and its application to the undergraduate college is here: \href{http://www.stern.nyu.edu/uc/codeofconduct}{Undergraduate College Conduct}. \textbf{Any violation of the a policies pertaining to Academic Integrity will result in a failing grade for the course.}
\end{itemize}

\subsubsection*{Students with disabilities}

If you have a qualified disability that requires academic accommodation during this course,
please contact the Moses Center for Students with Disabilities (CSD, 212-998-4980) and ask them to
send me a letter verifying your registration and outlining the accommodation they recommend.
If you need to take an exam at the CSD, you must submit a completed Exam Accommodations Form to them
at least one week prior to the scheduled exam time to be guaranteed accommodation.
